Polymers for Near-field Electrospinning with Spatial Control

### 2020-03-14 myPapers/NFES_Review/Polymers_for_Nearfield_Electrospinning_with_Spatial_Control/article.tex
organising my directories ...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Feature enabled:
%toc: yes
%bookmark: yes
%pagenum: yes
%text-layout: twocolumn
%endfloat: placeins
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
\makeatother
\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
\makeatletter
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
\makeatother
          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
\usepackage[section]{placeins}

\usepackage{etoolbox}

\usepackage{longtable}

@@

\makeatletter
\AtBeginDocument{\@ifpackageloaded{rotating}{\PassOptionsToPackage{figuresright}{rotating}}{\usepackage[figuresright]{rotating}}\setlength{\rotFPtop}{0pt plus 1fil}\setlength{\rotFPbot}{0pt plus 1fil}}
\makeatother

\makeatletter
 \AtBeginDocument{%
  \@ifpackagewith{endfloat}{figuresonly}
  {\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}}%true
  {\@ifpackagewith{endfloat}{tablesonly}{\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}%true
  {\@ifpackageloaded{endfloat}{\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}\DeclareDelayedFloatFlavor{sidewaystable}{table}\DeclareDelayedFloatFlavor{longtable}{table}\DeclareDelayedFloatFlavor{landscape}{table}}{}}%false
  }%false
  }
\makeatother

\usepackage{pdflscape}

@@

\bgroup
\fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
\makeatother 
\caption{{Electrohydro-dynamic techniques}}
\label{f-02e0e3cf88d6}
\end{figure}
\egroup

\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process. As Brown et al. \unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used). The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state. The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution. The apparatus used by Brown et al. \unskip~\cite{527120:13445499} is depicted in .

[TODO: draw an apparatus used for melt electrospinning].

Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.

@@

\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle [TODO: draw nested needles]. \unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers. Sun et al. \unskip~\cite{527120:13914312} addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core. Sun et al. state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning. The shell solution can be modified to make the core solution spunable. It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution. \unskip~\cite{527120:13914968}

Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle. On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles. \unskip~\cite{527120:13914748,527120:13914750}. As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector. With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate. The instability can be mitigated by adding additional ring electrodes between the spinneret and the grounded collector. \unskip~\cite{527120:13915304}

@@

The centrifugal force technique is applied to polymer solutions and melts. This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.  Efforts in centrifugal spinning are focused on drug delivery applications. Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach. Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.

@@

\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution. The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate. Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}.

[TODO: draw an apparatus used for solution blow spinning or melt blowing] \unskip~\cite{527120:13538056}.

Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning. Oliveira et al. \unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications. On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques. Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods. The fibers produced by electrospinning had thicker diameters and their size uniformity was higher in the fibers produced by solution blow spinning.

@@

[TODO: draw Figure apparatus used for solution blow spinning or melt blowing]

\subsubsection{Mechanical force}Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette. \unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications. \unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers. Touch-spinning comprises a rotating stage with an embedded glass rod. [TODO: draw touch spinning setup]. Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers. The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter. The increase in length causes the fiber surface are to increase and therefore making the polymer solution solvent to volatilize, ending with a dry fiber within the collector.

The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration. The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}

@@

[TODO: draw Figure apparatus used for microfluidic spinning]

Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.

\subsection{Nozzle-to-substrate distance}[TODO: draw FFES setup], depicts the typical setup for the conventional far-field electrospinning (FFES). As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}. When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process. The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}. The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.

In the intent to achieve controlled fiber deposition, Sun et al. \unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES). [TODO: draw NFES setup], describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line. Moreover, some mechanical influence is required to deposit fibers precisely. The mechanical force is introduced by moving collector. If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}. Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.

@@

\bgroup
\fixFloatSize{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}{\includegraphics{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}}{}
\makeatother 
\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130}.}}
\label{f-8e5a75d9ba17}
\end{figure}
\egroup

\section{Properties that Improve Accuracy of Nano-Fiber Deposition}
Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition. This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.

\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES. Low voltage near field electrospinning produces thinner fibers with lower voltages. Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching. Bisht et al. \unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.

-{\textgreater} A continuous method for controlled electrospinning of polymeric nano fibers on two-dimensional (2D) and three-dimensional (3D) substrates using low voltage near-field electrospinning (LV NFES). The method overcomes some of the drawbacks in more conventional near-field electrospinning by using a super elastic polymer ink formulation. The visco-elastic nature of our polymer ink enables continuous electrospinning at a very low voltage of 200 V, almost an order of magnitude lower than conventional NFES, thereby reducing bending instabilities and increasing control of the resulting polymer jet. In one application, polymeric nano fibers are freely suspended between micro structures of 3D carbon on Si substrates to illustrate wiring together 3D components in any desired pattern.{\textless}-

\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}-{\textgreater} A continuous near-field electrospinning (NFES) process has been developed to deposit solid nano fibers with orderly patterns over large areas. Before the onset of electrospinning, a bias voltage is applied to a semi-spherical shaped polymer droplet outside of a syringe needle, and a probe tip mechanically draws a single fiber from the droplet to initiate continuous NFES. Contrary to the conventional electrospinning process, we show that decreasing electrical field in continuous NFES results in smaller line width deposition, and nano fibers can be assembled into controlled complex patterns such as circular shapes and grid arrays on large and flat areas. {\textless}-

\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}-{\textgreater} Characterized the behavior of polymer jet from near-field electrospinning onto the ink-jet patterned paper with conductive Ag nano particles in order to form the controlled three-dimensional nano structures. Using ink-jet patterned paper with conductive ink as a collector, the polymer jet is induced to the pre patterned shape through the concentrated electric field caused by singularity between the spinneret and the printed patterns. Due to the electric field enhancement of the deposited electrospun fiber, an additionally spun fiber can be stacked on the deposited fibers directly. Therefore, the controlled three-dimensional nano/micro structures can be successfully realized by the proposed method. We characterized the deposition of the electrospun fiber according to the distance between the ink-jet printed pattern and the spinneret. In addition, the sharp edged three-dimensional micro-structures were fabricated by carrying out the electrospinning on the patterns with various angled edges. A CCD camera was used to observe the behavior of the polymer jet, and the SEM image was analyzed to confirm that the fibers are stacked as desired.

Uncover a new method for the preparation of bio-polymer scaffolds and demonstrate its potential for the development of organs with the aid of tissue engineering. Two novel nano-composite polymers, a non-biodegradable polyhedral oligomeric silsesquioxane-poly (carbonate-urea)urethane and a biodegradable polyhedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate-urea)urethane, have been subjected to flow in an electric field. Electrically forced micro-threading of the polymers occurs and a three-dimensional print-patterning device was used to deposit fine (⬍50 \ensuremath{\mu}m) threads of polymer according to a pre-designed architecture to prepare scaffolds. The technique can offer tremendous potential in the development of organs. {\textless}-

\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}-{\textgreater} Multinozzle electrospinning systems are designed to increase productivity, while near-field electrospinning (NFES) systems are designed to deposit solid nano fibers in a direct, continuous, and controllable manner. In this paper, several multinozzle NFES setups are tested. The experiment reveals that the deposition distance becomes larger when working distance and needle spacing increase, and the influence of voltage is relatively weaker. The deposition of double nozzle NFES has been studied with Coulomb's law and theoretical derivation has been verified by the experimental conclusion. The experiment result and theoretical derivation are helpful to get different distance of direct-written fibers by adjusting working distance or needle spacing to change distance of fibers largely and adjusting voltage to change distance slowly. Through these efforts, it is convenient to adjust the distance of straight fibers in multinozzle system. [1]

For large area micro/nano pattern printing, multi-nozzle electrohydrodynamic (EHD) printing setup is an efficient method to boost productivity in near-field electrospinning (NFES) process. And controlling EHD multi-jet accurate deposition under the interaction of nozzles and other parameters are crucial concerns during the process. The influence and sensitivity of various parameters such as the needle length, needle spacing, electrode-to-collector distance, voltage etc. on the direct-write patterning performance was investigated by orthogonal experiments with dual-nozzle NFES setup, and then the deposition distance estimated based on a novel model was com- pared with measurement results and proven. More controllable deposition distance and much denser of aligned nano fiber can be achieved by rotating the dual-nozzle setup. This study can be greatly contributed to estimate the deposition distance and helpful to guide the multi-nozzle NFES process to accurate direct-write pattern in manufacturing process in the future.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Feature enabled:
%toc: yes
%bookmark: yes
%pagenum: yes
%text-layout: twocolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
\makeatother
\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
\makeatletter
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
\makeatother
          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
\usepackage{etoolbox}

@@

@@

\bgroup
\fixFloatSize{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}{\includegraphics{images/514dfac6-849d-4905-8e40-7adfafc93b5f-uimg_ehd_techniques.png}}{}
\makeatother 
\caption{{Electrohydro-dynamic techniques}}
\label{f-02e0e3cf88d6}
\end{figure}
\egroup

\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process. As Brown et al. \unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used). The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state. The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution. The apparatus used by Brown et al. \unskip~\cite{527120:13445499} is depicted in Figure~\ref{f-1e9a6ae11444}.

\bgroup
\fixFloatSize{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}{\includegraphics{images/9f289b61-472d-4106-8f56-f160403f3ba0-uimg_metl_setup.png}}{}
\makeatother 
\caption{{Typical Melt Electrospinning Setup}}
\label{f-1e9a6ae11444}
\end{figure}
\egroup
Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.

@@

\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle, see Figure~\ref{f-e0d8f2eb18d4}. \unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers. Sun et al. \unskip~\cite{527120:13914312} addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core. Sun et al. state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning. The shell solution can be modified to make the core solution spunable. It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution. \unskip~\cite{527120:13914968}

\bgroup
\fixFloatSize{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}{\includegraphics{images/9d6b16c0-e5ec-4b60-adfa-e55a194e6694-uimg_nozzle.png}}{}
\makeatother 
\caption{{Needle configurations in coaxial electrospinning. (a) the outer needle encasing the inner; (b) the inner needle protruding from the outer; (c) both needles inline with each other;}}
\label{f-e0d8f2eb18d4}
\end{figure}
\egroup
Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle. On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles. \unskip~\cite{527120:13914748,527120:13914750}. As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector. With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate. The instability can be mitigated by adding additional ring electrodes between the spinneret and the grounded collector. \unskip~\cite{527120:13915304}

@@

\bgroup
\fixFloatSize{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}{\includegraphics{images/19c94c11-1ae0-47bd-95ef-4dc5ceedc20d-uimg_gyro_es.png}}{}
\makeatother 
\caption{{Typical setup used in pressurized gyration Processes}}
\label{f-7cf6ac702e28}
\end{figure}
\egroup
The centrifugal force technique is applied to polymer solutions and melts. This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.  Efforts in centrifugal spinning are focused on drug delivery applications. Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach. Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.

@@

\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution. The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate. Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}, see Figure~\ref{f-92361290d8c3} .

\bgroup
\fixFloatSize{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}{\includegraphics{images/87246522-4cf1-491f-a45f-cda541854d72-uimg_blow_es.png}}{}
\makeatother 
\caption{{Dispensing nozzle used for solution blow spinning or melt blowing. \unskip~\protect\cite{527120:13538056}}}
\label{f-92361290d8c3}
\end{figure}
\egroup
Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning. Oliveira et al. \unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications. On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques. Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods. The fibers produced by electrospinning had thicker diameters and their size uniformity was higher in the fibers produced by solution blow spinning.

@@

\subsubsection{Mechanical force}
\bgroup
\fixFloatSize{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}{\includegraphics{images/23a9bc42-4d02-4a78-a907-23aeeb2de68a-uimg_meches_process.png}}{}
\makeatother 
\caption{{Typical mechanical fiber drawing process}}
\label{f-432d16f420fb}
\end{figure*}
\egroup
Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette. \unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications. \unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers where the fiber is created by stretching the polymer precursor with a moving collector, as depicted in Figure~\ref{f-432d16f420fb}. Touch-spinning comprises a moving stage with an embedded glass rod (Figure~\ref{f-f17259e76303}). Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers. The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter. The increase in length causes the fiber surface are to increase and therefore making the polymer solution solvent to volatilize, ending with a dry fiber within the collector.

\bgroup
\fixFloatSize{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}{\includegraphics{images/c33e7bfe-18c6-4765-834e-a85f12cd2621-uimg_touch_process.png}}{}
\makeatother 
\caption{{Touch-spinning technique. First rod is attached to a rotating stage and a polymer solution droplet is administrated through a needle. Then the rotating rod 'touches' the polymer precursor. Finally, as the rod rotates, the polymer solution is stretched and creates a fiber between the rod and the needle.}}
\label{f-f17259e76303}
\end{figure*}
\egroup
The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration. The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}

@@

\bgroup
\fixFloatSize{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}{\includegraphics{images/efb1d6af-4f1a-4c34-9726-b0015b59e112-uimg_microfluid_setup.png}}{}
\makeatother 
\caption{{Microfluidic device used by Kang et al.\unskip~\protect\cite{527120:13656548}}}
\label{f-c0beae2757bf}
\end{figure}
\egroup
Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.

\subsection{Nozzle-to-substrate distance}
\bgroup
\fixFloatSize{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}{\includegraphics{images/3c63cd76-6542-45b7-aa5a-2f90200fecb4-uffes_vs_nfes.png}}{}
\makeatother 
\caption{{a) Typical Far-field Electrospinning (FFES) Setup. b) Typical Near-field Electrospinning (NFES) Setup.}}
\label{f-fbe88d27b932}
\end{figure*}
\egroup
Figure~\ref{f-fbe88d27b932}.a, depicts the typical setup for the conventional far-field electrospinning (FFES). As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}. When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process. The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}. The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.

In the intent to achieve controlled fiber deposition, Sun et al. \unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES),Figure~\ref{f-fbe88d27b932}, describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line. Moreover, some mechanical influence is required to deposit fibers precisely. The mechanical force is introduced by moving collector. If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}. Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.

@@

\section{Properties that Improve Accuracy of Nano-Fiber Deposition}
Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition. This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research. Table S1 is a collection of the relevant NFES process parameters and achieved fiber morphology.

Some differences have been discovered between LV-NFES and conventional NFES. Low voltage near field electrospinning produces thinner fibers with lower voltages. Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching. Bisht et al. \unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.

Bisht et al. \unskip~\cite{527120:11973130} reports a controlled technique to fabricate polymeric nano fibers in a continuous manner, using a low voltage setup. Their purpose is to find a workaround to the drawbacks of traditional NFES by using a superelastic polymer precursor, which allow continuous patterning without breaking. In low voltage near-field electrospinning (LV NFES), a visco-elastic polymer is used to allow continuous spinning at about 200$V $ . The decrease in voltage is prone to produce a controlled polymer jet by reducing the bending instabilities. The authors demonstrate the effectiveness of this technique with the fabrication of suspended fibers, see Figure~\ref{f-52c94fbe4526} .

\bgroup
\fixFloatSize{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}{\includegraphics{images/55cad0f8-ee25-40e9-96e0-390553fcf271-ubisht_0.png}}{}
\makeatother 
\caption{{Suspended nano fibers of 2 wt \% PEO at 300 V. (a) Six carbon posts connected by nano fibers. (b) Individual nano fiber suspended between the posts. (c) Close up of the suspended nano fiber. \unskip~\protect\cite{527120:11973130}}}
\label{f-52c94fbe4526}
\end{figure*}
\egroup
Chang et al. \unskip~\cite{527120:11974306} developed a scanning tip electrospinning (a continuous NFES) technique to write nano fibers with control patterning. Similar to Bisht et al. \unskip~\cite{527120:11973130}, they also demonstrate that the decrease in the applied electric field yields thinner fibers that can be controlled to develop circular shapes (Figure~\ref{f-9d0c3125e550}) and grids (Figure~\ref{f-32e7d8abb3aa}) on a flat surfaces.

\bgroup
\fixFloatSize{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}{\includegraphics{images/afadfb20-d115-4170-8ccf-cb53e9d8d64d-uchang_00.png}}{}
\makeatother 
\caption{{The three-character Cal is drawn on a silicon chip by a programmable x-y stage. \unskip~\protect\cite{527120:11974306}}}
\label{f-9d0c3125e550}
\end{figure}
\egroup

\bgroup
\fixFloatSize{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}{\includegraphics{images/6283d5c1-1602-46a7-80a6-96b40d0b22d7-uchang_01.png}}{}
\makeatother 
\caption{{A triangular grid pattern. \unskip~\protect\cite{527120:11974306}}}
\label{f-32e7d8abb3aa}
\end{figure}
\egroup
Kim et al. \unskip~\cite{527120:11974313} experimented with a NFES variation where the fiber deposition is guided by conductive rails, see Figure~\ref{f-927e96fb5537} . As stated by the authors, the induced electric field is enhanced by the conductive pattern, which allows the fibers to follow the desired deposition path. As the fibers are prone to follow the conductive pattern, additional fibers can be stacked on each other. The stacking process was successfully achieved in high electric field conditions at: 750$\mu m $ substrate to collector distance, and 600 $\mu m $ needle to rail (offset) distance, see  . (Applied voltage not explicitly specified for "straight line pattern" and stacking experiments, only stated the implementation of 1.9 $kV $ on "sharp-edged shapes pattern" experiments).

\bgroup
\fixFloatSize{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}{\includegraphics{images/0fd23deb-7631-4b09-8641-69fc6ac8a6b5-ukim_00.png}}{}
\makeatother 
\caption{{NFES setup for controlled fiber deposition on pre-patterned conductive electrodes. \unskip~\protect\cite{527120:11974313}}}
\label{f-927e96fb5537}
\end{figure*}
\egroup

\bgroup
\fixFloatSize{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}{\includegraphics{images/3c862704-5da9-4ed0-8616-d8562e9cc5f0-ukim_01.png}}{}
\makeatother 
\caption{{SEM and CCD camera images of stacked fibers on the conductive pattern when high electric field and low electric field were applied}}
\label{f-24b5148e8358}
\end{figure}
\egroup
Gupta et al.\unskip~\cite{527120:11974310} introduced a new technique to fabricate polymer scaffolds for tissue engineering applications and organ development. The authors implemented two polymer solutions, with POSS-PCU (polyhedral oligomeric silsesquioxane-poly(carbonate-urea)urethane, a non-biodegradable polymer precursor) and with POSS-PCL-PCU (poly- hedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate- urea)urethane, a biodegradable polymer precursor).

As described by Gupta et al.\unskip~\cite{527120:11974310}, the fiber deposition equipment is comprised by a stainless steel needle with a internal diameter of 750 $\mu m $ , connected to a high voltage power supply of up to 30 $k V $ with a deposition rate of about $\geq 1 \mu L min^{-1} $. The setup was embedded to a motorized collector capable of controlled programmable motions, see Figure~\ref{f-74de1f00848b}. The proposed technique was able to produce fibers of $150 \mu m $ in diameter with pre-designed patterns.
